Algebraic File Synchronization: Adequacy and Completeness

### 2017-11-23 p2/axioms.tex
Merged definitions

So that we can describe the effects of commands independently of filesystems,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
Sequences are also partial endofunctions on filesystems,
defined only if all commands they contain succeed in the given order.
The sequences of commands form a monoid, and, as usual,
we write $\emptyseq$ for the unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

\begin{mydef}[$\Dom{S}$ and $\Img{S}$]
For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$.
We write $\Img{S}$ to denote the image of the domain of the sequence $S$.
\end{mydef}

The following two relations 
echo the ones defined in \cite{NREC}.
In the definitions, $A,B,S,T$ stand for arbitrary sequences.

\begin{mydef}[$\eqext$]
% Relation in the algebra
We write $A\eqext B$, or $B$ \emph{extends} $A$,
% intended interpretation:
to mean that they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS\in\Dom{A}: A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
% preorder: reflexive and transitive
% patial order: reflexive, transitive and antisymmetric (aRb & bRa => a=b) TODO
In other words, $\eqext$ is a preorder, and also a precongruence.
\end{mydef}

\begin{mydef}[$\equiv$]
% Relation in the algebra
$A\equiv B$,
or $A$ and $B$ are \emph{equivalent,}
iff $A\eqext B$ and $B\eqext A$;
that is, $\equiv$ is the intersection of the preorder $\eqext$ with its inverse,
and so it is a congruence.
% symmetric: aRb <=> bRa
% reflexive: aRa
% transitive: aRb & bRC => aRc
% old inference rule: $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.
\end{mydef}

@@

\begin{mydef}[$\strext$]
We write $A\strext B$ if $A\eqext B$ and $A\nequiv B$.
In particular, we write $\wrks{A}$ if $A$ is defined on some filesystems.
\end{mydef}

>>>>

So that we can describe the effects of commands independently of filesystems,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the sequence is executed from left to right:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
Sequences are also partial endofunctions on filesystems,
defined only if all commands they contain succeed in the given order.
Sequences form a monoid, and, as usual,
we write $\emptyseq$ to denote the unit element, the empty sequence,
which is defined on all filesystems and, by definition, leaves all filesystems unchanged.
\end{mydef}

\begin{mydef}[$\Dom{S}$]
For a sequence of commands $S$, $\Dom{S}$ is the domain of $S$, that is,
the set of filesystems $S$ does not break.
\end{mydef}

The following two relations 
echo the ones defined in \cite{NREC}.
In the definitions, $A,B,S$ and $T$ stand for arbitrary sequences.

\begin{mydef}[$\eqext$, $\strext$ and $\equiv$]
% Relation in the algebra
We write $A\eqext B$, or say that $B$ \emph{extends} $A$,
% intended interpretation:
to mean that they behave in the same way
on any filesystem $A$ does not break:
$\forall \FS\in\Dom{A}:\,A\aFS=B\aFS$.
% old inference rule: $ A\eqext B \Rightarrow S\cc A\cc T\eqext S\cc B\cc T$,
We can also see that $A\eqext B$ and $S\eqext T$ implies $A\cc S\eqext B\cc T$.
% symmetric:     aRb <=> bRa
% antisymmetric: aRb & bRa => a=b
% reflexive:     aRa
% transitive:    aRb & bRC => aRc
% preorder:      reflexive, transitive
% partial order: reflexive, transitive, antisymmetric
% equivalence:   reflexive, transitive, symmetric
% congruence:    https://en.wikipedia.org/wiki/Congruence_relation
% precongruence: congruence of a preorder
In other words, $\eqext$ is a preorder, and also a precongruence. % TODO

% Relation in the algebra
We write $A\equiv B$,
or say that $A$ and $B$ are \emph{equivalent,}
iff $A\eqext B$ and $B\eqext A$;
that is, $\equiv$ is the intersection of the preorder $\eqext$ with its inverse,
and so it is a congruence. % TODO
% old inference rule: $ A\equiv B \Rightarrow S\cc A\cc T\equiv S\cc B\cc T $.

Finally, we write $A\strext B$ to mean $A\eqext B$ and $A\nequiv B$.
In particular, we write $\wrks{A}$
to mean that $\Dom{A}$ is not empty, that is, if $A$ is defined on some filesystems.
\end{mydef}

@@
